testtreefallposition

### 2021-08-20 R/DESIGNATION_DRAFT.Rmd
loggingsimulation function and doc refresh

inventory = addtreedim(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "0"
objective = 20
diversification = TRUE
specieslax = FALSE
objectivelax = FALSE
advancedloggingparameters = loggingparameters()
# MainTrail

>>>>

inventory = addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)) #3539 rows (Paracou: 3620 rows)
speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "0"
objective = 20
diversification = TRUE
specieslax = FALSE
objectivelax = FALSE
advancedloggingparameters = loggingparameters()
# MainTrail

### 2021-08-20 R/Draft_spatio.Rmd
loggingsimulation function and doc refresh

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))

>>>>

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)

inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)

### 2021-08-20 R/testtreefallposition.Rmd
loggingsimulation function and doc refresh

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```

>>>>

inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```
